Blame and Coercion: Together Again for the Second Time

### 2019-10-17 paper.tex
reorder syntax of cast calculus
revise static sem. of cast calc

\begin{figure}
	Syntax
	\[
	\begin{array}{rclr}
	\stxrule{T}{types}{
		\star \mid{}
		P
	}
	\stxrule{P}{pre-types}{
		\POOunit \mid
		\POOfun{T_1}{T_2} \mid
		\POOprod{T_1}{T_2} \mid
		\POOsum{T_1}{T_2}
	}
	\stxrule{c}{casts}{
		\cOOcast{T_1}{l}{T_2}
	}
	\stxrule{e}{terms}{
		\eOOvar{x} \mid{}
		\eOOsole{} \mid{}
		\eOOlam{T_1}{T_2}{x}{e} \mid
		\eOOapp{e_1}{e_2}
	}
	\stxrulecont{
		\eOOcons{e_1}{e_2} \mid
		\eOOcar{e} \mid
		\eOOcdr{e}
	}
	\stxrulecont{
		\eOOinl{e} \mid
		\eOOinr{e} \mid
		\eOOcase{e_1}{e_2}{e_3}
	}
	\stxrulecont{
		\eOOcast{e}{c} \mid
		\eOOblame{l}
	}
	\stxrule{I}{injectable types (\lazyD)}{
		P
	}
	\stxrule{I}{injectable types (\lazyUD)}{
		\POOunit \mid
		\POOfun{\star}{\star} \mid
		\star \times \star \mid
		\star + \star
	}
	\stxrule{v}{values}{
		\vOOfun{\rho}{x}{e} \mid
		\vOOtt{} \mid
		\vOOcons{v_1}{v_2} \mid
		\vOOinl{v} \mid
		\vOOinr{v} \mid		
		\vOOcast{v}{c}
	}
	\stxrule{o}{observations}{
		\oOOinj \mid
		\oOOsole \mid
		\oOOfun \mid
		\oOOcons \mid
		\oOOinl \mid
		\oOOinr \mid
		\oOOblame{l}
	}
	\end{array}
	\]

@@

Let $ e $ range over terms. Most terms are standard. We annotate the codomain 
of lambda abstractions explicitly because we need it when evaluating cast 
calculus with hypercoercion. We have two additional terms: cast expressions and 
blame expressions. Cast expressions insert runtime type checks. And blame 
expressions raise an error. The end of \figref{fig:blame-static} shows the 
typing rules for the additional terms.

>>>>

\begin{figure}
	Syntax
	\[
	\begin{array}{rclr}
	\stxrule{T}{types}{
		\star \mid{}
		P
	}
	\stxrule{P}{pre-types}{
		\POOunit \mid
		\POOfun{T_1}{T_2} \mid
		\POOprod{T_1}{T_2} \mid
		\POOsum{T_1}{T_2}
	}
	\stxrule{c}{casts}{
		\cOOcast{T_1}{l}{T_2}
	}
	\stxrule{e}{terms}{
		\eOOvar{x} \mid{}
		\eOOsole{} \mid{}
		\eOOlam{T_1}{T_2}{x}{e} \mid
		\eOOapp{e_1}{e_2} \mid
		\eOOcons{e_1}{e_2} \mid
		\eOOcar{e} \mid
		\eOOcdr{e}
	}
	\stxrulecont{
		\eOOinl{e} \mid
		\eOOinr{e} \mid
		\eOOcase{e_1}{e_2}{e_3} \mid
		\eOOcast{e}{c} \mid
		\eOOblame{l}
	}
	\stxrule{v}{values}{
		\vOOtt{} \mid
		\vOOfun{\rho}{x}{e} \mid
		\vOOcons{v_1}{v_2} \mid
		\vOOinl{v} \mid
		\vOOinr{v} \mid		
		\vOOcast{v}{c}
	}
	\stxrule{I}{injectable types (\lazyD)}{
		P
	}
	\stxrule{I}{injectable types (\lazyUD)}{
		\POOunit \mid
		\POOfun{\star}{\star} \mid
		\star \times \star \mid
		\star + \star
	}
	\stxrule{o}{observations}{
		\oOOinj \mid
		\oOOsole \mid
		\oOOfun \mid
		\oOOcons \mid
		\oOOinl \mid
		\oOOinr \mid
		\oOOblame{l}
	}
	\end{array}
	\]

@@

Let $ e $ range over terms. Most terms are standard. We annotate the codomain 
of lambda abstractions explicitly because we need it when evaluating cast 
calculus with hypercoercion. We have two additional terms: cast expressions and 
blame expressions. Cast expressions insert runtime type checks. And blame 
expressions raise an error. The typing rules for the additional terms are
straightforward.

Let $ v $ range over values. A value is either the unit, a function (a 
closure), a pair, a left injection, a right injection, or a 
casted value. As shown 
by the value typing rules, if the target type of a casted value is the dynamic 
type, the underlying value must be of an injectable type. The definition of 
injectable types depends on blame strategies: for the \lazyD\ strategy, every 
pre-type is injectable; for the \lazyUD\ strategy, a pre-types is injectable if 
and only if all its sub-parts are the dynamic type. If the target type of a 
casted value is a pre-type, the type of the underlying value must have the same 
type constructor.
